Visualising metagenome differences

### 2023-11-21 analysis/metagenome.Rmd
yay

```{r setup, message=FALSE}
library(tidyverse)
library(microshades)
library(ggtext)
library(scales)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

@@

There we go :) Which MAGs are those?
```{r}
amph_pos_tax_cat |> filter(str_detect(Species, 'Acidihalobacter')) |> knitr::kable()

@@

```{r}
amph_pos_tax_cat |> filter(str_detect(Family, 'Ectothiorhodospiraceae'))
```
Are these in the GTDB classification?
```{r}
amph_pos_tax |> filter(str_detect(family, 'Ectothiorhodospiraceae'))
```
Nope!

@@

```{r}
count_diffs |> filter(`Posidonia australis` <100) |> head() |> knitr::kable()
```

@@

```{r}
genessplit |> filter(gene == 'acdS') |> left_join(amph_pos_tax, by=c('sample', 'MAG'), multiple = 'any') |> knitr::kable()
```
Lots of unknown taxonomies :(

@@

### nifH
```{r}
tmp <- genessplit |> filter(str_detect(gene, 'nifH') & str_detect(Tissue, 'Root')) |> 
  mutate(gene_class = case_when(str_detect(gene, 'nifH') ~ 'nifH')) |> 
  group_by(Sample_species, Sample_replicate) |> count(gene_class) 
tmp  
```

@@

```{r}
tmp <- genessplit |> filter(str_detect(gene, 'sctC') & str_detect(Tissue, 'Root')) |> 
  mutate(gene_class = case_when(str_detect(gene, 'sctC') ~ 'sctC')) |> 
  group_by(Sample_species, Sample_replicate) |> count(gene_class) 
tmp  
```

@@

```{r}
tmp <- genessplit |> filter(str_detect(gene, 'acdS') & str_detect(Tissue, 'Root')) |> 
  mutate(gene_class = case_when(str_detect(gene, 'acdS') ~ 'acdS')) |> 
  group_by(Sample_species, Sample_replicate) |> count(gene_class) 
tmp 
```

>>>>

```{r setup, message=FALSE}
library(tidyverse)
library(DT)
library(microshades)
library(ggtext)
library(scales)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

@@

There we go :) Which MAGs are those?
```{r}
amph_pos_tax_cat |> filter(str_detect(Species, 'Acidihalobacter')) |> datatable()

@@

```{r}
amph_pos_tax_cat |> filter(str_detect(Family, 'Ectothiorhodospiraceae'))|> datatable()
```
Are these in the GTDB classification?
```{r}
amph_pos_tax |> filter(str_detect(family, 'Ectothiorhodospiraceae'))|> datatable()
```
Nope!

@@

```{r}
count_diffs |> filter(`Posidonia australis` <100) |> datatable()
```

@@

```{r}
genessplit |> filter(gene == 'acdS') |> left_join(amph_pos_tax, by=c('sample', 'MAG'), multiple = 'any') |> datatable()
```
Lots of unknown taxonomies :(

@@

### nifH
```{r}
tmp <- genessplit |> filter(str_detect(gene, 'nifH') & str_detect(Tissue, 'Root')) |> 
  mutate(gene_class = case_when(str_detect(gene, 'nifH') ~ 'nifH')) |> 
  group_by(Sample_species, Sample_replicate) |> count(gene_class) 
tmp  |> datatable()
```

@@

```{r}
tmp <- genessplit |> filter(str_detect(gene, 'sctC') & str_detect(Tissue, 'Root')) |> 
  mutate(gene_class = case_when(str_detect(gene, 'sctC') ~ 'sctC')) |> 
  group_by(Sample_species, Sample_replicate) |> count(gene_class) 
tmp  |> datatable()
```

@@

```{r}
tmp <- genessplit |> filter(str_detect(gene, 'acdS') & str_detect(Tissue, 'Root')) |> 
  mutate(gene_class = case_when(str_detect(gene, 'acdS') ~ 'acdS')) |> 
  group_by(Sample_species, Sample_replicate) |> count(gene_class) 
tmp |> datatable()
```
